Syntax and Semantics of Abstract Binding Trees

### 2015-11-12 paper.tex
[paper] use \mathbb{1} from bbmath

By the Grothendieck construction
$\Iso{\Grothendieck{}{\Operators}}{\Comma{*}{\Operators}}$ we have a category of
elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are paired
diagrams:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\Pair{\Upsilon}{a}}
      \arrow[r, "\Pair{\rho}{f}", swap]
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, sep = small, ampersand replacement = \&]
    \& *
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]
We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  &\IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}&&\,\mathrel{\ {{:}}}\,&&\IMode{\SCtx\times\Discrete{\Arities}\to\Sets}\\
  &\IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}&&\,=\,\ && %
    \OMode{%
      \MkSet{
        \vartheta\in\Pair{\Upsilon}{a}
        \mid
        {\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
        \Pair{\Upsilon}{a}
      }
    }
\end{alignat*}

>>>>

By the Grothendieck construction
$\Iso{\Grothendieck{}{\Operators}}{\Comma{\mathbb{1}}{\Operators}}$ we have a category of
elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are paired
diagrams:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\Pair{\Upsilon}{a}}
      \arrow[r, "\Pair{\rho}{f}", swap]
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, sep = small, ampersand replacement = \&]
    \& \mathbb{1}
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]
We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  &\IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}&&\,\mathrel{\ {{:}}}\,&&\IMode{\SCtx\times\Discrete{\Arities}\to\Sets}\\
  &\IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}&&\,=\,\ && %
    \OMode{%
      \MkSet{
        \vartheta\in\Pair{\Upsilon}{a}
        \mid
        {\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
        \Pair{\Upsilon}{a}
      }
    }
\end{alignat*}
